---
title: "How to use roller package"
author: "Horton Papa"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(roller)
```

#Motivation

The package `roller` was created to simulate rolling a multi sided device with an associated probability for each side. This device can be a coin at its simplest form, a die, or a 100 sided object. The package then creates a table of the outcome of the roll dependent on the specified probability of success of each side.

###Functions in package
- `device()`: creates a multisided object
- `roll()`: simulates the roll of an object
- `summary()`: creates a summary of performed rolls
- `plot()`: Creates a barplot of the relative frequencies of resulting rolls

#Usage
##Create an object to be tossed

The function `device()` allows the user to create an object that can be used to be rolled.

###Basic device using `device()`

The `device()` function has a default output of a basic, fair two sided object:

```{r}
basic_device = device()
basic_device
```

###Object with multiple sides

You can specify as many sides as you want with respective probabilities:

```{r}
multi_side = device(sides = letters[1:8], 
                    prob = rep(1/8, 8))
multi_side
```


##"Roll" the device with `roll()`

To roll the device simply call the roll function and specify how many times you want to perform the roll and the output will return the respective output of each roll

```{r}
# roll the basic device
basic_10 = roll(basic_device, 
                times = 10)

basic_10

#roll the multi sided device
multi_300 = roll(multi_side,
                 times = 300)
multi_300

```

###View basic summary of output of rolls

The package has been provided with summary method for class "rolls." The summary displays a tally and the proportion of the outcome of each side.

```{r}
#display summary of basic device roll
summary(basic_10)

#display summary of multi sided device roll
summary(multi_300)
```


###Plot method

The plot method for the rolls displays a barplot of the relative frequencies of the rolls; to do this simply call `plot()`

```{r, fig.width= 6, fig.height=5}
#plot multi_300
plot(multi_300)
```

###Other Methods/operations

####Extract roll value

Similar to extracting a value from  a vector, use `[]` notation to extract desired value

```{r}
#extract 7th roll of basic_10
basic_10[7]

#extract 213th roll value of multi_300
multi_300[213]
```

####Replace the value of a roll 

Similarly as above, the package uses vector operation to extract values and replace it with the deisred value:
```{r}
#replace 7th roll of basic_10 with 2
basic_10[7] = 2
basic_10[7]

#replace 213th roll with a "c"
multi_300[213] = "c"
multi_300[213]
```

####Add more rolls

To add more rolls simply use the `+` operator to add the desired number of rolls

```{r}
# add 8 more rolls to basic_10
basic_18 = basic_10 + 8
basic_18

# add 100 more rolls to multi_300
multi_400 = multi_300 + 100
multi_400
```







